Supplementary material

### 2017-10-24 Manuscript/ms.tex
Abstract text

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}

>>>>

Our ability to effectively prevent the transmission of the dengue virus through targeted control of its vector, \emph{Aedes aegypti}, depends critically on our understanding of the link between mosquito abundance and human disease risk.
The mosquito and clinical surveillance data necessary to elucidate this link are widely collected, but have yet to be coupled with a modeling framework that accounts for the complex non-linear mechanisms involved in transmission, in particular the critical bottleneck imposed by mosquito mortality.
Here we develop a differential equation model of dengue transmission and embed it in a Bayesian hierarchical framework that allows us to estimate latent time series of mosquito demographic rates from mosquito trap counts and dengue case reports from the city of Vitoria, Brazil.
We then use the fitted model to explore the optimal timing of targeted adult control during the year.
We find that control is most effective when deployed in the third week of the year, as mosquito abundance nears its peak and dengue transmission begins to ramp up.
Intervening at this time disrupts transmission and prevents the amplification and feedback that leads to large outbreaks of disease, an insight not possible without the underlying mechanistic model.
Though the ability of mosquito surveillance to predict human disease is often limited, this highlights the utility of this surveillance when integrated into a larger modeling framework.
Grounding this modeling famework in the actual mechanisms of transmission will help to establish more effective and efficient dengue control policies that allow us to better target mosquitoes that are most responsible for continuing disease spread.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author summary}
